quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-15 paper-quollr.Rmd
Start add the algorith steps

@@

Add a Figure explaining the steps

>>>>

hex_grid_poly_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice)

hex_centroids_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff")  +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

wireframe_scurve <- ggplot() +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

@@

```{r, eval=knitr::is_latex_output()}
scurve_umap_plt + hex_grid_poly_scurve + 
  hex_centroids_scurve + wireframe_scurve + 
  plot_layout(ncol = 5)
```

### 2025-05-15 paper-quollr.tex
Added intro image
Added one projection for S-curve data
Start add the algorith steps

@@

Add a Figure explaining the steps

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-22-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-23-1}

@@

@@

>>>>

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-3-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-4-1}

@@

@@

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-26-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-27-1}
